\documentclass{article}
\usepackage[utf8]{inputenc}

\title{MAT454 Notes}
\author{Jad Elkhaleq Ghalayini}
\date{January 15 2020}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{cancel}
\usepackage{mathabx}

\usepackage[margin=1in]{geometry}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem*{claim}{Claim}

\newcommand{\brac}[1]{\left(#1\right)}
\newcommand{\sbrac}[1]{\left[#1\right]}
\newcommand{\eval}[3]{\left.#3\right|_{#1}^{#2}}
\newcommand{\ip}[2]{\left\langle#1,#2\right\rangle}
\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\prt}[2]{{\frac{\partial {#1}}{\partial {#2}}}}
\def\ries{{\hat{\mbb{C}}}}
\newcommand{\reals}{\mbb{R}}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}

\DeclareMathOperator{\Res}{Res}

\begin{document}

\maketitle

Let's, as we usually do, consider a holomorphic function \(f(z)\) in an open set \(\Omega \subseteq \mbb{C}\). Last time, we showed that \(f\) has a convergent power series expansion in any open disc in \(\Omega\) (centered at the center of the disc). For example, around \(a = 0 \in \Omega\), we can write
\[f(z) = \sum_{n = 0}^\infty a_nz^n\]
Writing \(z = re^{i\theta}\), we get
\[f(re^{i\theta}) = \sum_{n = 0}^\infty a_nr^ne^{in\theta}\]
We can write out the following formula for these Fourier coefficients:
\[a_nr^n = \frac{1}{2\pi}\int_0^{2\pi}e^{-in\theta}f(re^{i\theta})d\theta\]
Today we're going to be looking at the consequences of this formula. First of all, this formula gives a simple but useful upper bound on \(a_n\): if we take the maximum absolute value of \(f\) along the circle of radius \(r\), written
\[M(r) = \sup_\theta|f(re^{i\theta})|\]
we get
\[|a_n| \leq \frac{M(r)}{r^n}\]
These are called \textbf{Cauchy's inequalities}. These have some important consequences, like \textbf{Liouville's theorem}: a bounded holomorphic function on all of \(\mbb{C}\) is a constant. How does this follow? Well, if \(c\) is the upper bound of \(f\) on \(\mbb{C}\), we have each
\[\forall r \in \reals^+, M(r) \leq c \implies |a_n| \leq \frac{M(r)}{r^n} \leq \frac{c}{r^n}\]
Hence, for \(n > 0\), \(0 \leq a_n \leq \epsilon\) for all \(\epsilon > 0\), implying \(a_n = 0\). It follows that \(f = a_0 = c\), a constant. Another consequence is that we can write, for any \(r\)
\[f(0) = a_0 = a_0r^0 = \frac{1}{2\pi}\int_0^{2\pi}f(re^{i\theta})d\theta\]
This generalizes readily to stating that holomorphic functions satisfy the \textbf{Mean Value Property (MVP)}:
\[f(\text{center of disk}) = \ \text{mean value on boundary}\]
Another property which we won't prove is the \textbf{Maximum Modulus Principle (MMP)}: if \(f\) is a continuous complex-valued function on an open \(\Omega \subseteq \mbb{C}\) with the MVP, then it satisfies the MMP, that is, if \(|f|\) has a local maximum at a point \(a\) of \(\Omega\), then \(f\) is constant in a neighborhood of \(a\).

We can use this to prove \textbf{Schwarz's Lemma}:
\begin{theorem}[Schwarz's Lemma]
Suppose \(f(z)\) is holomorphic in \(|z| < 1\), \(f(0) = 0\) and \(|f(z)| < 1\). Then
\begin{enumerate}

  \item \(|f(z)| \leq |z|\) if \(|z| < 1\)

  \item If \(|f(z_0)| = |z_0|\) at some \(z_0 \neq 0\), then \(f(z) = \lambda z\) for some \(|\lambda| = 1\).

\end{enumerate}
\end{theorem}
We recall a sketch of the proof
\begin{proof} (Sketch)
By the convergent power series expansion, \(g(z) / z\) is holomorphic, and can hence have the maximum modulus principle applied to it.
\end{proof}
So let's spend a little time looking at functions with the MVP in general. Continuous functions with the MVP are precisely the \underline{harmonic functions}. The real and imaginary parts of a complex valued function with the MVP also satisfy the MVP. A real valued harmonic function \(g\) is locally the real part of a holomorphic function, uniquely determined up to addition of a constant:
\[
\prt{^2g}{z\partial\bar{z}} = 0 \implies \prt{g}{z} \ \text{holomorphic}
\]
Therefore, \(\prt{g}{z}\) locally has primitive \(f\), defined up to a constant. Since \(g\) is real valued, we can write
\[df = \prt{g}{z}dz, \quad d\bar{f} = \prt{g}{\bar{z}}d\bar{z}\]
Hence,
\[d(f + \bar{f}) = dg \implies g = 2\Re f + \ \text{const}\]
So harmonic functions satisfy the MVP and MMP, and conversely, a continuous function in an open set \(\Omega \subseteq \mbb{C}\) satisfying the MVP is harmonic. Just a couple of words as to why this is true, as this is really something that you should review: this comes from the solution to what's called the Dirichlet problem for a disk. What is this problem? It says that, given any continuous function \(f\) on the boundary of a disk \(|z| < r\), you can extend it to a continous function \(F\) on the whole disk which is harmonic on the interior.

\end{document}
